Appendix

### 2025-03-18 manuscript_rmarkdown/manuscript_appendix.Rmd
Update central normality test.

\begin{definition}[Empirical central normality test]
The null-hypothesis is defined as: $\mathcal{H}_0: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j = 0$

@@

\begin{definition}[Empirical central normality test statistic]
Let $\alpha$ be the significance level for the empirical central normality test.
Let $m$ be the number of elements of $\mathbf{R}_{\text{c}}$

The test statistic is then $\tau_{\text{ecn}, \alpha, n, \kappa} = \frac{1}{m}\sum_{r_j \in \mathbf{R}_{\text{c}}}r_j$.

@@

Critical values for the test statistic of the empirical central normality test 
are found in Table \ref{tab:empirical-central-normality-critical-statistic}. 
The null-hypothesis should be rejected at significance level $\alpha$ if 
$\tau_{\text{ecn}, \alpha, n, \kappa} \geq \tau_{\text{ecn}, \alpha, n, \kappa, \text{critical}}$.

@@

gof_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = FALSE
)

usethis::use_data(
  gof_lookup_table, 
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\text{ecn},\alpha, n, \kappa = 0.70}$ for
empirical central normality at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

\midrule
5     & 25.28 & 22.17 & 17.46 & 13.15 & 10.48 & 8.32 & 6.62 & 4.93 & 2.24 \\
10    & 21.11 & 18.16 & 13.66 & 10.14 &  8.67 & 7.59 & 6.74 & 5.89 & 4.12 \\
20    & 14.93 & 12.96 &  9.97 &  7.71 &  6.77 & 6.11 & 5.56 & 5.02 & 3.97 \\
50    &  9.69 &  8.49 &  6.59 &  5.20 &  4.63 & 4.22 & 3.91 & 3.58 & 2.99 \\
100   &  6.92 &  6.06 &  4.71 &  3.73 &  3.32 & 3.04 & 2.83 & 2.59 & 2.20 \\
200   &  4.89 &  4.29 &  3.35 &  2.66 &  2.37 & 2.17 & 2.02 & 1.87 & 1.60 \\
500   &  3.12 &  2.73 &  2.12 &  1.69 &  1.51 & 1.39 & 1.29 & 1.19 & 1.02 \\
1000  &  2.19 &  1.92 &  1.50 &  1.20 &  1.07 & 0.98 & 0.92 & 0.85 & 0.73 \\
2000  &  1.56 &  1.37 &  1.06 &  0.85 &  0.76 & 0.70 & 0.65 & 0.60 & 0.52 \\
5000  &  0.99 &  0.86 &  0.67 &  0.54 &  0.48 & 0.44 & 0.41 & 0.38 & 0.32 \\
10000 &  0.69 &  0.61 &  0.48 &  0.38 &  0.34 & 0.31 & 0.29 & 0.27 & 0.23 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

>>>>

\begin{definition}[Central normality test]
The null-hypothesis is defined as: $\mathcal{H}_0: \sum_{r_j \in \mathbf{R}_{\text{c}}}r_j = 0$

@@

\begin{definition}[Central normality test statistic]
Let $\alpha$ be the significance level for the empirical central normality test.
Let $m$ be the number of elements of $\mathbf{R}_{\text{c}}$

The test statistic is then $\tau_{\alpha, n, \kappa} = \frac{1}{m}\sum_{r_j \in \mathbf{R}_{\text{c}}}r_j$.

@@

Critical values for the test statistic of the central normality test 
are found in Table \ref{tab:empirical-central-normality-critical-statistic}. 
The null-hypothesis should be rejected at significance level $\alpha$ if 
$\tau_{\alpha, n, \kappa} \geq \tau_{\alpha, n, \kappa, \text{critical}}$.

@@

central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = FALSE
)

empirical_central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = FALSE,
  with_outliers = TRUE
)

usethis::use_data(
  central_normality_lookup_table,
  empirical_central_normality_lookup_table,
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
central normality at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

\midrule
5     & 10.49 & 13.15 & 17.46 & 22.17 & 25.28 & 27.90 & 29.93 & 31.88 & 34.58 \\
10    &  8.67 & 10.14 & 13.66 & 18.16 & 21.11 & 23.91 & 26.96 & 31.44 & 48.04 \\
20    &  6.77 &  7.71 &  9.97 & 12.96 & 14.93 & 16.70 & 18.24 & 20.33 & 25.24 \\
50    &  4.63 &  5.20 &  6.59 &  8.49 &  9.69 & 10.81 & 11.87 & 13.14 & 16.11 \\
100   &  3.32 &  3.73 &  4.71 &  6.06 &  6.92 &  7.71 &  8.45 &  9.39 & 11.31 \\
200   &  2.37 &  2.66 &  3.35 &  4.29 &  4.89 &  5.46 &  6.00 &  6.67 &  8.02 \\
500   &  1.51 &  1.69 &  2.12 &  2.73 &  3.12 &  3.48 &  3.84 &  4.24 &  5.30 \\
1000  &  1.07 &  1.20 &  1.50 &  1.92 &  2.19 &  2.44 &  2.68 &  3.01 &  3.68 \\
2000  &  0.76 &  0.85 &  1.06 &  1.37 &  1.56 &  1.74 &  1.90 &  2.11 &  2.55 \\
5000  &  0.48 &  0.54 &  0.67 &  0.86 &  0.99 &  1.10 &  1.20 &  1.34 &  1.64 \\
10000 &  0.34 &  0.38 &  0.48 &  0.61 &  0.69 &  0.77 &  0.84 &  0.93 &  1.15 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = TRUE,
  with_outliers = TRUE
)
